Fig3

### 2020-05-07 analysis/figure-2.Rmd
now with correaltions WGCNA and DESEq in Fig 3

### Candidate gene functions

```{r}
candidateboxplot <- function(whichtissue, whichgenes, whichsex){

  p <- candidatevsd %>%
    filter(tissue %in% whichtissue,
          gene %in% whichgenes,
          sex %in% whichsex) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    ggplot(aes(x = treatment, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    facet_wrap(~sex,  nrow = 1) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          axis.title.y = element_text(face = "italic"),
          axis.text.x = element_blank(),
          axis.ticks = element_blank()) +
    labs(y = whichgenes,
         x = NULL) +
    geom_signif(comparisons = list(c( "control", "bldg"),
                                 c( "bldg", "lay"),
                                 c( "lay", "inc.d3"),
                                 c("inc.d3", "inc.d9"),
                                 c( "inc.d9", "inc.d17"),
                                 c( "inc.d17", "hatch"),
                                 c("hatch", "n5"),
                                 c( "n5", "n9")),  
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0)

  return(p)
}

scattercorrelations <- function(df, gene1, gene2, mylinecolor, myxlab, myylab){
  p <- ggplot(df, aes(x = gene1, y = gene2)) +
    labs(subtitle = " ", x = myxlab, y = myylab) + 
    scale_color_manual(values = allcolors) +
    geom_smooth(method = "glm",  color = mylinecolor) +
    geom_point(aes(color = treatment))  +
    theme_B3() +  
    theme(axis.title = element_text(face = "italic"), 
            legend.position = "none") +
    stat_cor( size = 2)
  return(p)
}

>>>>

## Figure

### 2020-05-07 analysis/figure-3.Rmd
now with correaltions WGCNA and DESEq in Fig 3

@@

# subset PRL vsd

@@

@@

PRLDEGs <- allDEG2 %>%
  filter(tissue == "pituitary", comparison == "lo vs. hi PRL   ",
         direction == "hi") %>%
  arrange(desc(comparison))
PRLDEGs

envDEGs <- allDEG2 %>%
  filter(tissue == "pituitary", comparison == "eggs vs. chicks",
         direction == "chicks") %>%
  arrange(desc(comparison))
envDEGs

## genes WGCNA prl module

PRLgenes <- read_csv("../results/PRLmodule.csv") %>% pull(x)

candidatevsd <- getcandidatevsd(PRLgenes, "pituitary", sexlevels)

df <- candidatevsd %>%
    pivot_wider(names_from = gene, values_from = counts) %>%
    select(-sex,-tissue, -treatment, -samples) %>%
    correlate() %>%
  focus(PRL)  %>%
  arrange(rowname)
df

## top correlations
c <- df %>%
  arrange(desc(PRL)) %>% 
  head(10)  %>%
  mutate(PRLrounded = round(PRL, 2))%>% 
  ggplot(aes(x = reorder(rowname, PRL), y = PRL)) +
  geom_bar(stat = "identity") +
  theme_B3() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(x = " ", y = "Correlation with PRL", subtitle = "Top 10 co-regulated genes") +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0))

@@

a1 <- plotpc12(pca1f, pca2f, pca1f$treatment, allcolors, "Female pituitary gene expression", " ")   
a2 <- plotprolactin(PRLpitF, PRLpitF$counts, "PRL", " ") + theme(axis.text.x = element_text())

a3 <- plotpc12(pca1m, pca2m, pca1m$treatment, allcolors, "Male pituitary gene expression", NULL)
a4 <- plotprolactin(PRLpitM, PRLpitM$counts, "PRL", " ") + theme(axis.text.x = element_text())

a <- plot_grid(a1,a2,a3,a4, labels = c("A"), label_size = 8, rel_heights = c(1.1,1))

@@

fig3 <- plot_grid(a, bc, nrow = 2, rel_heights = c(1,1))
fig3

>>>>

pca1 <- subsetmakepca("pituitary", charlevels, sexlevels)	
pca2 <- makefvizdf("pituitary", charlevels, sexlevels)

@@

# Hi Lo PRL and WGCNA PRL

@@

### WGCNA prolactin module

```{r}
## genes WGCNA prl module

WGCNAgenes <- read_csv("../results/PRLmodule.csv") %>% pull(x)

WGCNAvsd <- getcandidatevsd(WGCNAgenes, "pituitary", sexlevels)

@@

PRLDEGs <- allDEG2 %>%
  filter(tissue == "pituitary", comparison == "lo vs. hi PRL   ",
         direction == "hi") %>%
  arrange(desc(logpadj))
PRLDEGs

envDEGs <- allDEG2 %>%
  filter(tissue == "pituitary", comparison == "eggs vs. chicks",
         direction == "chicks") %>%
  arrange(desc(logpadj))
envDEGs

hilogenes <- PRLDEGs %>% head(20) %>% distinct(gene) %>% pull(gene)
eggchickgenes <- envDEGs %>% head(20) %>% distinct(gene) %>% pull(gene)

hypothesisDEGs <- c(hilogenes, eggchickgenes, WGCNAgenes) %>% unique()

candidatevsd <- getcandidatevsd(hypothesisDEGs, "pituitary", sexlevels)

#candidateboxplot("pituitary", c("PNOC"), "female") + labs(x = NULL )  + theme( strip.text = element_blank())
#candidateboxplot("pituitary", c("KPNA2"), "male") + labs(x = NULL )  + theme( strip.text = element_blank())

pithilo <- makecorrdf("female", "pituitary", hilogenes)
piteggchick <- makecorrdf("female", "pituitary", eggchickgenes)
pitWGCNA <- makecorrdf("female", "pituitary", WGCNAgenes[1:20])
```

@@

a1 <- plotpc12(pca1, pca2, pca1$treatment, allcolors, "Pituitary gene expression", " ")   
a2 <- plotprolactin(PRLpit, PRLpit$counts, "PRL", " ") + theme(axis.text.x = element_text())

a <- plot_grid(a1,a2, labels = c("A"), label_size = 8)

@@

d1 <-plotcorrplot(piteggchick, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 eggs vs. chicks DEGs")
d2 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 lo vs. PRL DEGs")
d3 <-plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes from WGCNA module with PRL")

d <- plot_grid(d1,d2,d3, nrow = 1, align = "h", labels = c("D"), label_size = 8)

fig3 <- plot_grid(a, bc, d, nrow = 3, rel_heights = c(1.2,2,1.8))
fig3
